Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*

### 2019-04-05 analyses/reproduce_analyses.Rmd
added treatment effects. Results are counterintuitive though. I see no clear evidence of clutch size on selection gradients, even though it clearly differs between treatments in the trait-fitness relationships.

```{r Food-web model, cache=TRUE}
foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
    Foodweb:(sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
    Foodweb:(sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

@@

```{r Food-web alpha coefficients}
foodweb_bind <- as_tibble(boot_foodweb_model$t) #bind_cols(
  #as_tibble(boot_linear_foodweb_model$t),
  #select(as_tibble(boot_foodweb_model$t), `FoodwebComplex:sc.Diam.2`:`FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1`) # only retain nonlinear coefficients from full model
#)

>>>>

```{r Food-web contrast model, cache=TRUE}
foodweb_contrast_model <- glmer(
  gall_survival ~ 
    Foodweb*(sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
    Foodweb*(sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
    Foodweb*(sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
summary(foodweb_contrast_model) # Chi-square tests below correspond to Wald z-tests in summary

drop1(foodweb_contrast_model, test="Chisq") # marginal effect of sqrt.Pref^2

# manually testing lower order terms as I've already scaled them to make them mostly orthrogonal
anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb:sc.Diam.1), test="Chisq")
anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb:sc.log.Clutch.1), test="Chisq") # clear effect
anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb:sc.sqrt.Pref.1), test="Chisq")
anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb), test="Chisq") # clear effect

# Revised food-web model after removing non-significant terms
foodweb_model <- glmer(
  gall_survival ~ 
    Foodweb + 
    (sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
    Foodweb:sc.log.Clutch.1 +
    (sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
    Foodweb:sc.sqrt.Pref.2 +
    (sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
summary(foodweb_model)
```

```{r Food-web model, cache=TRUE, eval=FALSE}
foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
    Foodweb:(sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
    Foodweb:(sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

```{r Food-web model old, eval=FALSE}

car::vif(foodweb_model) # GVIF vary between 1.4 and 4, which I don't like

# we get a clear reduction in VIF when we specify a simpler model.
foodweb_contrast_model <- glmer(
  gall_survival ~ 
    Foodweb + (sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
    Foodweb:sc.log.Clutch.1 +
    (sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
    (sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))#,
  #contrast = list(Foodweb = "contr.sum"))
summary(foodweb_contrast_model)
car::vif(foodweb_contrast_model) # after specifying contr.sum, most values are less than 2 (max 2.5)

@@

```{r Food-web alpha coefficients}
foodweb_bind <- as_tibble(boot_foodweb_model$t) %>%
  rename(FoodwebComplex = `(Intercept)`,
         `FoodwebComplex:sc.Diam.1` = sc.Diam.1,
         `FoodwebComplex:sc.log.Clutch.1` = sc.log.Clutch.1,
         `FoodwebComplex:sc.sqrt.Pref.1` = sc.sqrt.Pref.1,
         `FoodwebComplex:sc.Diam.2` = sc.Diam.2,
         `FoodwebComplex:sc.log.Clutch.2` = sc.log.Clutch.2,
         `FoodwebComplex:sc.sqrt.Pref.2` = sc.sqrt.Pref.2,
         `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1` = `sc.Diam.1:sc.log.Clutch.1`,
         `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1` = `sc.Diam.1:sc.sqrt.Pref.1`,
         `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1` = `sc.log.Clutch.1:sc.sqrt.Pref.1`) %>%
  # set trait-fitness relationships equal for appropriate terms
  mutate(`FoodwebSimple:sc.Diam.1` = `FoodwebComplex:sc.Diam.1`,
         #`FoodwebSimple:sc.log.Clutch.1` # we estimate food-web effects for this term
         `FoodwebSimple:sc.sqrt.Pref.1` = `FoodwebComplex:sc.sqrt.Pref.1`,
         `FoodwebSimple:sc.Diam.2` = `FoodwebComplex:sc.Diam.2`,
         `FoodwebSimple:sc.log.Clutch.2` = `FoodwebComplex:sc.log.Clutch.2`,
         #`FoodwebSimple:sc.sqrt.Pref.2` # we estimate food-web effects for this term
         `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` = `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1`,
         `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` = `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1`,
         `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` = `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1`)
  #bind_cols(
  #as_tibble(boot_linear_foodweb_model$t),
  #select(as_tibble(boot_foodweb_model$t), `FoodwebComplex:sc.Diam.2`:`FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1`) # only retain nonlinear coefficients from full model
#)
